\sysfull

### 2018-08-04 paper/asplos19/relatedwork.tex
add Rachet task splitting differences

Mementos left the possibility of non-volatile state becoming inconsistent with
volatile state saved in the checkpoint, rendering in-place writes to data
structures in non-volatile memory unsafe~\cite{mspcdino}.
%
DINO~\cite{dino} addressed the consistency problem by selectively versioning
non-volatile state within the checkpoints. Ratchet~\cite{ratchet} ensured
consistency by placing a checkpoint at the beginning of each idempotent region
in the code.  Clank~\cite{hicks_isca_2017} ensured consistency with custom
hardware that dynamically tracks read-after-write dependencies in memory
accesses and checkpoints on demand. The consistency problem was also
approached with a combination of undo and redo logging in
software~\cite{baghsorkhi_cgo_2018}.
%
Just-in-time checkpointing, such as Quickrecall~\cite{quickrecall} and
Hibernus++~\cite{hibernusplusplus}, eschews inconsistency by saving all
volatile state immediately before power failure and halting the execution.
Unlike \sys, such systems rely on introspection hardware to monitor supply
voltage and on accurate worst-case bounds on checkpoint cost.

>>>>

Mementos left the possibility of non-volatile state becoming inconsistent with
volatile state saved in the checkpoint, rendering in-place writes to data
structures in non-volatile memory unsafe~\cite{mspcdino}.
%
DINO~\cite{dino} addressed the consistency problem by selectively versioning
non-volatile state within the checkpoints. Ratchet~\cite{ratchet} ensured
consistency by placing a checkpoint at the beginning of each idempotent region
in the code. Ratchet has a similar technique to task splitting with some essential differences: (i) It does not need to handle non-volatile memory accesses, since it assumes a unified non-volatile memory, whereas \sys has to save the volatile pages in non-volatile memory; (ii) The checkpoint is of a fixed size, while \sys privatize variant number of memory pages.  Clank~\cite{hicks_isca_2017} ensured consistency with custom
hardware that dynamically tracks read-after-write dependencies in memory
accesses and checkpoints on demand. The consistency problem was also
approached with a combination of undo and redo logging in
software~\cite{baghsorkhi_cgo_2018}.
%
Just-in-time checkpointing, such as Quickrecall~\cite{quickrecall} and
Hibernus++~\cite{hibernusplusplus}, eschews inconsistency by saving all
volatile state immediately before power failure and halting the execution.
Unlike \sys, such systems rely on introspection hardware to monitor supply
voltage and on accurate worst-case bounds on checkpoint cost.
